
Examples which are installed with EUTelescope can be run immediately. The only additional requirement is you have access to the DESY afs. A brief outline of some examples with be given below to show what can be done with the fitter. All examples in jobsub/examples/GBL directory in EUTelescope. A step by step guide of what parameters to change in the config is given in the README for each example. The name is black is the name given in the examples directory.

\begin{description} 
\item[noDUTExample] This example demostrates the use of the fitter with magnetic fields and varying beam energies.
\item[Quad] Quad module with reference DUT at the DESY testbeam 
\item[QuadSLAC]  Quad module and reference DUT at the SLAC testbeam.
\item[Pixels] High radiation length enviroment using the gear file to describe dead material. Two APIX devices at DESY testbeam.
\item[mappingAPIX] Two APIX DUTs using the mapping processor between channel number and geometric cluster position.
\item[mappingAPIXSLAC] This is the same as the other mapping example but at SLAC and with highly irradiated sensors. The highly irradiated sensors make the reconstruction much harder.
\item[SCT] Strip example which has been used for detailed efficiency measurements. This example contains the ROOT output formats which include TBMon.
\item[StripAlibava] ATLAS12 strip device using the alibava system as readout. High radiation length downstream causes larger beam divergences than expected at DESY beam.
\item[X0] The use of the kink angle estimation is demonstrated here. The results of this example should be investigated more fully. However the track fitting and alignment is completed. 
\end{description} 